Fan, splint and branching rules.

### 2011-10-13 AffineLieAlgebras/Splints/paper.tex

\documentclass[12pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{amsmath,amssymb,amsthm}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}

\newtheorem{Def}{Definition}[section]
\newtheorem{Cnj}[Def]{Conjecture}
\newtheorem{Prop}[Def]{Property}
\newtheorem{example}{Example}
\begin{document}

\title{Fan, splint and branching rules.}

@@

\begin{abstract}
Splint of root system of simple Lie algebra appears naturally in the study of (regular) embedding of reductive subalgebra. It can be used to derive branching rules. We show that the use of splint drastically simplifies the derivation of branching functions. 
\end{abstract}

\section{Introduction}
\label{sec:Introduction} 
Splint $\phi$ of root system $\Delta_1$ to root system $\Delta$ is a bijective map of roots of $\Delta_{1}$ to (proper) subset of $\Delta$ which commutes with the addition in $\Delta_{1}$ and $\Delta$. 
\begin{equation*}
\phi:\Delta_1 \longrightarrow \Delta
\end{equation*}
\begin{equation*}
\phi \circ \alpha + \beta =\phi \circ \alpha + \phi \circ \beta,
\,\,\, \alpha,\beta \in \Delta_1
\end{equation*}

Note that image $Im(\phi)$ is not required to have the properties of root system except the addition rules equivalent to the addition rules in $\Delta_{1}$ (for pre-images). The term {\it splint} was introduce in paper \cite{richter2008splints} where the classification of splints for simple Lie algebras was obtained. The conjecture of the connection splint with injection fan was stated in the same paper. 
The fan $\Gamma \subset \Delta$ as the subset of root system describing recurrent properties of branching coefficients for maximal embeddings  was introduced in \cite{lyakhovsky1996rra}. Injection fan is an efficient tool for the study of branching rules. This construction was generalized to non-maximal embeddings and infinite-dimensional Lie algebras in  \cite{2010arXiv1007.0318L, ilyin812pbc}.

In present paper we study the connection of splint with the injection fan of regular embedding of reductive subalgebra ${\mathfrak a}$. We show that (under certain conditions described in section \ref{sec:stems and multiplicity functions}) splint is a natural tool for the reduction of simple Lie algebra $\gf$-modules to the modules of subalgebra $\af\rightarrow\gf$. The use of this tool allows us to state the main result of the present paper -- the one-to-one relationship between weight multiplicities of irreducible modules of splint and branching coefficients for the reduction $L^{\mu}_{{\mathfrak g}\downarrow {\mathfrak a}}$.

\section{Injections and splints}
\label{sec:Injections and splints}

Consider a simple Lie algebra $\mathfrak{g}$ and its regular
subalgebra $\mathfrak{a}\longrightarrow \mathfrak{g%
}$ such that $\mathfrak{a}$ is a reductive subalgebra $\mathfrak{a
\subset g}$ with correlated root spaces:
$\mathfrak{h}_{\mathfrak{a}}^{\ast }\subset
\mathfrak{h}_{\mathfrak{g }}^{\ast }$. Let $\mathfrak{a}^S$ be a
semisimple summand of $\mathfrak{a}$, this means that
$\mathfrak{a}=\mathfrak{a}^S \oplus \mathfrak{a}(1)\oplus
\mathfrak{a}(1)\oplus \dots$. We shall consider $\mathfrak{a}^S$
to be a proper regular subalgebra and $\mathfrak{a}$ to be the
maximal subalgebra with $\mathfrak{a}^S$ fixed that is the rank
$r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.

@@

$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
i$-th (resp. $j$-th) simple root for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a%
}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots
,r_{\mathfrak{a}^S}\right) $;

@@

$\cal{E}$ (resp. $\cal{E}_{\frak{a}} $) \ --- the formal algebra;

@@

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right)
\quad
$
(resp.
$
R_{\frak{a}}:
=\prod_{\alpha \in \Delta_{\frak{a}}^{+}}
\left( 1-e^{-\alpha }\right)
$
) --- the Weyl
denominator.

Let $L^{\mu }$ be completely reducible with respect to $\frak{a}$,
\begin{equation*}
L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
\end{equation*}
\begin{equation}
\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
\label{branching1}
\end{equation}
For the modules we are interested in the Weyl formula for $\mathrm{ch}%
\left( L^{\mu }\right) $ can be written in terms of singular
elements \cite {humphreys1997introduction}
\begin{equation*}
\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon
(w)e^{w(\mu +\rho )-\rho },
\end{equation*}
namely,
\begin{equation}
\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right)
}}{\Psi ^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right)
}}{R}. \label{Weyl-Kac2}
\end{equation}
The same is true for submodules $\mathrm{ch}\left(
L_{\frak{a}}^{\nu }\right) $ in (\ref{branching1})
\begin{equation*}
\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi
_{\frak{a}}^{\left(
\nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
}^{\left( \nu \right) }}{R_{\frak{a}}},
\end{equation*}
with
\begin{equation*}
\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
}}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
\end{equation*}

Applying formula (\ref{Weyl-Kac2}) to the branching rule
(\ref{branching1}) we get the relation connecting the singular
elements $\Psi ^{\left( \mu \right) }$ and $\Psi
_{\frak{a}}^{\left( \nu \right) }$ :
\begin{eqnarray}
 \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu
+\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })}
&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{%
\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{\frak{a}})-\rho _{%
\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}}^{+}}(1-e^{-\beta })},
\notag  \label{eq:4} \\
\frac{\Psi ^{\left( \mu \right) }}{R}
&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}%
}^{\left( \nu \right) }}{R_{\frak{a}}}.
\label{singular main}
\end{eqnarray}

In \cite
{2010arXiv1007.0318L} it was proven that branching coefficients $b_{\xi
}^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
\hookrightarrow \frak{g}$ are subject to the set of recurrent relations:
\begin{equation}
\begin{array}{c}
b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right.  \\
\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
}}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
}\right) .
\end{array}
\label{recurrent rel}
\end{equation}
where $\frak{a}_{\perp }$ is the subalgebra determined by the roots of $\frak{g}$ orthogonal to roots of $\frak{a}$
\begin{eqnarray}
\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
\label{delta a ort}
\end{eqnarray}
\begin{eqnarray}
\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
\qquad
\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }
\end{eqnarray}
and $\pi$ is the projection operator. When the injection is maximal the projection becomes trivial and the relation (\ref{recurrent rel}) is simplified:
\begin{equation}
\begin{array}{c}
b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in W}\epsilon (u) \delta _{\xi -\gamma _{0}, u(\mu +\rho )-\rho }+\right.  \\
\left. +\sum_{\gamma \in \Gamma _{\frak{a}\rightarrow \frak{g}%
}}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
}\right) .
\end{array}
\label{recurrent relation max}
\end{equation}
The recursion is goverened by the set $\Gamma _{\frak{a}%
\rightarrow \frak{g}}$ called the injection fan. The latter is defined by the
carrier set $\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the
coefficient function $s(\xi )$
\begin{equation*}
\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}:=\left\{
\xi \in P_{\frak{a}}|s(\xi )\neq 0\right\}
\end{equation*}
appearing in the expansion
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\frak{a}}^{+}}\left( 1-e^{
-\alpha }\right) =-\sum_{\gamma \in P_{%
\frak{a}}}s(\gamma )e^{-\gamma };\quad
\label{product}
\end{equation}

Now we remind two definitions introduced in \cite{richter2008splints}
\begin{Def}
Suppose $\Delta_0$ and $\Delta$ are root systems with the corresponding weight lattices $P_0$ and $P$.  Then $\phi$ is an ``embedding'', 
\begin{equation}
\phi:\left\{
\begin{array}{l}
\Delta_0\hookrightarrow\Delta,\\
P_0 \hookrightarrow P,
 \end{array}
\right.
\end{equation}
if \\
\noindent
(a) it injects $\Delta_0$ in $\Delta$, and \\
\noindent
(b) acts homomorphically with respect to the vector groups in $P_0$ and $P$:
$$\phi(\gamma)=\phi(\alpha)+\phi(\beta)$$
for any triple $\alpha,\beta,\gamma\in P_0$ such that $\gamma=\alpha+\beta$.
\end{Def}
$\phi$ induces an injection of formal algebras $ :{\cal{E}}_0 \longrightarrow \cal{E}$ and for the image ${\cal{E}}_i=Im_{\phi}\left( {\cal{E}}_0\right)$ one can consider its inverse
$\phi^{-1}:{\cal{E}}_i \longrightarrow {\cal{E}}_0$.

 Notice that one must distinguish two classes of embeddings: when the scalar product (defined by the Killing form) in the root space $P_0$ is invariant with respect to $\phi$ and when it is not $\phi$-invariant. The first embedding is called "metric" 
, the second -- "nonmetric". 
\begin{Def}
A root system $\Delta$ "splinters'' as $(\Delta_1,\Delta_2)$ if there are two embeddings
$\phi_1:\Delta_1\hookrightarrow\Delta$ and $\phi_2:\Delta_2\hookrightarrow\Delta$
where (a) $\Delta$ is the disjoint union of the images of $\phi_1$ and $\phi_2$ and
(b) neither the rank of $\Delta_1$ nor the rank of $\Delta_2$ exceeds the rank of $\Delta$.
\end{Def}
It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$ and we shall denote this by $\Delta \approx (\Delta_1,\Delta_2)$.
Each component $\Delta_1$ and $\Delta_2$ is a "stem'' of the splint $(\Delta_1,\Delta_2)$.

@@

To demonstrate the relations between these instruments consider the case where
one of the stems $\Delta_1=\Delta_{\frak{a}}$ is a root system of a regular reductive subalgebra  $\frak{a}\hookrightarrow\frak{g}$. Then the second stem is $\Delta_{\frak{s}}:=\Delta_2=\Delta \setminus \Delta _{\frak{a}}$ can be translated into the product (\ref{product}) and defines the injection fan $\Gamma_{\frak{a}\hookrightarrow\frak{g}}$.

Thus we see that
\begin{Cnj}
Each splint of the type $\Delta \approx (\Delta_{\frak{a}},\Delta_{\frak{s}})$ defines an injection fan with the carrier $\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ fixed by the product
\begin{equation}
\prod_{\beta \in  \Delta _{\frak{s}}^{+}}\left( 1-e^{
-\beta }\right) =-\sum_{\gamma \in P} s(\gamma )e^{-\gamma }\quad
\label{splint product}
\end{equation}
\end{Cnj}
In this case we say that the subalgebra $\frak{a}\hookrightarrow\frak{g}$ splinters $\Delta$ (and call $\frak{a}$ the "splinting subalgebra" of $\frak{g}$). In
\cite{richter2008splints} the splints are classified (see Appendix) and in the first three types one can easily see that one of the stems corresponds to a splinting subalgebra.

\section{How stems define multiplicity functions}
\label{sec:stems and multiplicity functions}

In this Section we consider the situation where  the splinting subalgebra is "larger"
than the Lie algebra $\frak{s}$ defined by the root system $\Delta_{\frak{s}\,0}=CoIm_{\phi} \left( \Delta_{\frak{s}}\right)$
(the details will be given below). In such a case to find branching coefficients for a splinting 
injection $\frak{a}\hookrightarrow\frak{g}$ means to find weight multiplicities for an irreducible $\frak{s}$-module $L^{\nu}_{\frak{s}}$ with 
the fixed highest weight $\nu$. Notice that $\frak{s}$ must not be a subalgebra of $\frak{g}$.

Let us return to relation (\ref{singular main}) and multiply both sides by $R_{\frak{a}}$: 
\begin{eqnarray}
 \frac{1}{\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })}\Psi_{\frak{g}} ^{\left( \mu \right) }
&=&
\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\Psi _{\frak{a}%
}^{\left( \nu \right) }.
\label{singular main-2}
\end{eqnarray}
Here the first factor in the l.h.s. is the inverse of the fan $\Gamma _{\frak{a}%
\rightarrow \frak{g}}$. 
Consider the highest weight module $L^{\nu}_{\frak{s}}$. An embedding
$\phi:\Delta_{\frak{s}\,0} \longrightarrow \Delta_{\frak{g}} $  sends the singular element         $\Psi_{\frak{s}} ^{\left( \nu \right)}$ into $ \Psi_{\frak{g}} ^{\left( \mu \right) }$.
Applying the inverse morphism $\phi^{-1}$ to the product 
$\left(\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })\right)^{-1}\phi\left(\Psi_{\frak{s}} ^{\left( \nu \right)}\right)$  
 one obtains the character of the module $L^{\nu}_{\frak{s}}$,

>>>>

\documentclass[12pt]{article}
\usepackage{amsfonts}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb,amsthm}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[english]{babel}

%TCIDATA{OutputFilter=Latex.dll}
%TCIDATA{LastRevised=Mon Oct 10 18:16:16 2011}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{CSTFile=article.cst}

\newtheorem{Def}{Definition}[section]
\newtheorem{Cnj}[Def]{Conjecture}
\newtheorem{Prop}[Def]{Property}
\newtheorem{example}{Example}[section]

%\input{tcilatex}

\begin{document}
\title{Fan, splint and branching rules.}

@@

\begin{abstract}
Splint of root system of simple Lie algebra appears naturally in
the study of (regular) embeddings of reductive subalgebras. It can
be used to derive branching rules. We show that application of
splint properties drastically simplifies calculations of
branching coefficients.
\end{abstract}

\section{Introduction}
\label{sec:Introduction} Splint $\phi$ of a root system $\Delta_1$
into a root system $\Delta$ is a bijective map of roots of
$\Delta_{1}$ to (proper) subset of $\Delta$ which commutes with
vector composition law in $\Delta_{1}$ and $\Delta$.
\begin{equation*}
\phi:\Delta_1 \longrightarrow \Delta
\end{equation*}
\begin{equation*}
\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
\,\,\, \alpha,\beta \in \Delta_1
\end{equation*}

Note that the image $Im(\phi)$ must not inherit the root system
properties except the addition rules equivalent to the addition
rules in $\Delta_{1}$ (for pre-images). The term {\it splint} was
introduced by D. Richter in  \cite{richter2008splints} where the
classification of splints for simple Lie algebras was obtained.
There was also mentioned that the notion of splint must have tight
connections with the injection fan approach. The fan $\Gamma
\subset \Delta$ was
introduced in \cite{lyakhovsky1996rra} as the subset of root system describing recurrent
properties of branching coefficients for maximal embeddings  . Injection fan is an
efficient tool to study branching rules. Later this construction
was generalized to non-maximal embeddings and infinite-dimensional
Lie algebras in \cite{2010arXiv1007.0318L, ilyin812pbc}.

In the present paper we study the connection of splint with
injection fan for regular embeddings of reductive subalgebras
${\mathfrak a}\longrightarrow {\mathfrak g}$. We show that (under
certain conditions described in section \ref{sec:stems and
multiplicity functions}) splint is a natural tool to study
reduction properties of simple Lie algebra ${\mathfrak g}$-modules
with respect to a subalgebra ${\mathfrak a}\longrightarrow
{\mathfrak g}$. Using this tool we obtain the main result of the
present paper -- the one-to-one correspondence between weight
multiplicities in irreducible modules of splint and branching
coefficients for a reduced module $L^{\mu}_{{\mathfrak
g}\downarrow {\mathfrak a}}$.

\section{Injections and splints}

\label{sec:Injections and splints}

Consider a simple Lie algebra $\mathfrak{g}$ and its regular subalgebra $%
\mathfrak{a}\longrightarrow \mathfrak{g}$ such that $\mathfrak{a}$ is a
reductive subalgebra $\mathfrak{a
\subset g}$ with correlated root spaces: $\mathfrak{h}_{\mathfrak{a}}^{\ast
}\subset \mathfrak{h}_{\mathfrak{g }}^{\ast }$. Let $\mathfrak{a}^S$ be a
semisimple summand of $\mathfrak{a}$, this means that $\mathfrak{a}=%
\mathfrak{a}^S \oplus \mathfrak{u}(1)\oplus \mathfrak{u}(1)\oplus \dots$. We
shall consider $\mathfrak{a}^S$ to be a proper regular subalgebra and $%
\mathfrak{a}$ to be the maximal subalgebra with $\mathfrak{a}^S$ fixed that
is the rank $r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.

@@

$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
i$-th (resp. $j$-th) simple root for $\frak{g}$ $\left( \mathrm{{resp.}\frak{%
a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
^S}\right) $;

@@

$\mathcal{E}$ (resp. $\mathcal{E}_{\frak{a}} $) \ --- the formal algebra;

@@

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) \quad $
(resp. $R_{\frak{a}}: =\prod_{\alpha \in \Delta_{\frak{a}}^{+}} \left(
1-e^{-\alpha }\right) $ ) --- the Weyl denominator.

Let $L^{\mu }$ be completely reducible with respect to $\frak{a}$,
\[
L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
\]
\begin{equation}
\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
\label{branching1}
\end{equation}
For the modules we are interested in the Weyl formula for $\mathrm{ch}\left(
L^{\mu }\right) $ can be written in terms of singular elements \cite
{humphreys1997introduction}
\[
\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
)-\rho },
\]
namely,
\begin{equation}
\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
\label{Weyl-Kac2}
\end{equation}
The same is true for submodules $\mathrm{ch}\left( L_{\frak{a}}^{\nu
}\right) $ in (\ref{branching1})
\[
\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left(
\nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
}^{\left( \nu \right) }}{R_{\frak{a}}},
\]
with
\[
\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
}}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
\]

Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
we get the relation connecting the singular elements $\Psi ^{\left( \mu
\right) }$ and $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
\begin{eqnarray}
\frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho )-\rho }}{\prod_{\alpha \in
\Delta ^{+}}(1-e^{-\alpha })} &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu
}^{(\mu )}\frac{\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{%
\frak{a}})-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}%
}^{+}}(1-e^{-\beta })},  \nonumber  \label{eq:4} \\
\frac{\Psi ^{\left( \mu \right) }}{R} &=&\sum_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}}^{\left( \nu \right) }}{R_{%
\frak{a}}}.  \label{singular main}
\end{eqnarray}

In \cite{2010arXiv1007.0318L} it was proven that branching coefficients $%
b_{\xi }^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
\hookrightarrow \frak{g}$ are subject to the set of recurrent relations:
\begin{equation}
\begin{array}{c}
b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right. \\
\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
}}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
}\right) .
\end{array}
\label{recurrent rel}
\end{equation}
where $\frak{a}_{\perp }$ is the subalgebra determined by the roots of $%
\frak{g}$ orthogonal to roots of $\frak{a}$
\begin{eqnarray}
\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
\label{delta a ort}
\end{eqnarray}
\begin{eqnarray}
\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
\qquad \widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }
\end{eqnarray}
and $\pi$ is the projection operator. When the injection is maximal the
projection becomes trivial and the relation (\ref{recurrent rel}) is
simplified:
\begin{equation}
\begin{array}{c}
b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in W}\epsilon (u) \delta _{\xi -\gamma _{0}, u(\mu +\rho )-\rho
}+\right. \\
\left. +\sum_{\gamma \in \Gamma _{\frak{a}\rightarrow \frak{g}}}s\left(
\gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right) }\right) .
\end{array}
\label{recurrent relation max}
\end{equation}
The recursion is goverened by the set $\Gamma _{\frak{a}\rightarrow \frak{g}}
$ called the injection fan. The latter is defined by the carrier set $%
\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the coefficient
function $s(\xi )$
\[
\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}:=\left\{ \xi \in P_{%
\frak{a}}|s(\xi )\neq 0\right\}
\]
appearing in the expansion
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\frak{a}}^{+}}\left( 1-e^{
-\alpha }\right) =-\sum_{\gamma \in P_{\frak{a}}}s(\gamma )e^{-\gamma };\quad
\label{product}
\end{equation}

Now we remind two definitions introduced in \cite{richter2008splints}

\begin{Def}
Suppose $\Delta _{0}$ and $\Delta $ are root systems with the corresponding
weight lattices $P_{0}$ and $P$. Then $\phi $ is an ``embedding'',
\begin{equation}
\phi :\left\{
\begin{array}{l}
\Delta _{0}\hookrightarrow \Delta , \\
P_{0}\hookrightarrow P,
\end{array}
\right.
\end{equation}
if \newline
\noindent (a) it injects $\Delta _{0}$ in $\Delta $, and \newline
\noindent (b) acts homomorphically with respect to the vector groups in $%
P_{0}$ and $P$:
\[
\phi (\gamma )=\phi (\alpha )+\phi (\beta )
\]
for any triple $\alpha ,\beta ,\gamma \in P_{0}$ such that $\gamma =\alpha
+\beta $.
\end{Def}

$\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
\longrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
_i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.

Notice that one must distinguish two classes of embeddings: when the scalar
product (defined by the Killing form) in the root space $P_0$ is invariant
with respect to $\phi$ and when it is not $\phi$-invariant. The first
embedding is called "metric" , the second -- "nonmetric".

\begin{Def}
A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if
there are two embeddings $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
\phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the
disjoint union of the images of $\phi _{1}$ and $\phi _{2}$ and (b) neither
the rank of $\Delta _{1}$ nor the rank of $\Delta _{2}$ exceeds the rank of $%
\Delta $.
\end{Def}

It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$
and we shall denote this by $\Delta \approx (\Delta_1,\Delta_2)$. Each
component $\Delta_1$ and $\Delta_2$ is a "stem'' of the splint $%
(\Delta_1,\Delta_2)$.

@@

To demonstrate the relations between these instruments consider the case
where one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ is a root subsystem
in $\Delta $.

Splint $\Delta \approx (\Delta _{1},\Delta _{2})$ is called ''injective'' if
one of its stems, say $\Delta _{1}=\Delta _{\frak{a}}$ , is a root subsystem
in $\Delta $ corresponding to a regular reductive subalgebra $\frak{a}%
\hookrightarrow \frak{g}$.

In case of injective splint the second stem $\Delta _{\frak{s}}:=\Delta
_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product (%
\ref{product}) and defines an injection fan $\Gamma _{\frak{a}%
\hookrightarrow \frak{g}}$.

Thus we see that

\begin{Cnj}
Each injective splint $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})
$ defines an injection fan with the carrier $\left\{ \xi \right\} _{\frak{a}%
\rightarrow \frak{g}}$ fixed by the product
\begin{equation}
\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)
=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}
\end{equation}
\end{Cnj}

In this case we say that the subalgebra $\frak{a}\hookrightarrow \frak{g}$
splinters $\Delta $ (and call $\frak{a}$ the ''splinting subalgebra'' of $%
\frak{g}$). In \cite{richter2008splints} splints are classified (see Appendix there)
and the first three types of them are injective.

\section{How stems define multiplicity functions}

\label{sec:stems and multiplicity functions}

In this Section we consider the situation where the splinting subalgebra is
''larger'' than the Lie algebra $\frak{s}$ defined by the root system $%
\Delta _{\frak{s}\,0}=CoIm_{\phi }\left( \Delta _{\frak{s}}\right) $ (the
details will be given below). In such a case to find branching coefficients
for a splinting injection $\frak{a}\hookrightarrow \frak{g}$ means to find
weight multiplicities for an irreducible $\frak{s}$-module $L_{\frak{s}%
}^{\nu }$ with fixed highest weight $\nu $. Notice that $\frak{s}$ must not
be a subalgebra of $\frak{g}$.

Let us return to relation (\ref{singular main}) and multiply both sides by $%
R_{\frak{a}}$:
\begin{equation}
\frac{1}{\prod_{\beta \in \Delta _{\frak{s}}^{+}}(1-e^{-\beta })}\Psi _{%
\frak{g}}^{\left( \mu \right) }=\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu
}^{(\mu )}\Psi _{\frak{a}}^{\left( \nu \right) }.
\label{singular main-2}
\end{equation}
Here the first factor in the l.h.s. is the inverse of the fan $\Gamma _{%
\frak{a}\rightarrow \frak{g}}$. Consider the highest weight module $L_{\frak{%
s}}^{\nu }$. An embedding $\phi :\Delta _{\frak{s}\,0}\longrightarrow \Delta
_{\frak{g}}$ sends the singular element $\Psi _{\frak{s}}^{\left( \nu
\right) }$ into $\Psi _{\frak{g}}^{\left( \mu \right) }$. Applying the
inverse morphism $\phi ^{-1}$ to the product $\left( \prod_{\beta \in \Delta
_{\frak{s}}^{+}}(1-e^{-\beta })\right) ^{-1}\phi \left( \Psi _{\frak{s}%
}^{\left( \nu \right) }\right) $ one gets the character of the module $L_{%
\frak{s}}^{\nu }$,

\begin{equation}
\phi ^{-1}\left( \frac{1}{\prod_{\beta \in \Delta _{\frak{s}%
}^{+}}(1-e^{-\beta })}\phi \left( \Psi _{\frak{s}}^{\left( \nu \right)
}\right) \right) =\frac{1}{\prod_{\beta \in \Delta _{\frak{s}\left( 0\right)
}^{+}}(1-e^{-\beta })}\Psi _{\frak{s}}^{\left( \nu \right) }=\mathrm{ch}%
\left( L_{\frak{s}}^{\nu }\right) .  \label{inverse for stem}
\end{equation}
Our task is to prove that the singular element $\Psi _{\frak{g}}^{\left( \mu
\right) }$ contains the element $\Psi _{\frak{s}}^{\left( \xi \right) }$ for
a module $L_{\frak{s}}^{\xi }$ uniquely defined by $L_{\frak{g}}^{\mu }$ and
that the branching coefficients $b_{\nu }^{(\mu )}$ in the r.h.s. of (\ref
{singular main-2}) coincide with multiplicities $m_{\zeta }^{\left( \xi
\right) }$ of the corresponding weights in $\mathcal{N}_{\frak{s}}^{\xi }$ .
